%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letter]{deedy-resume}

\begin{document}

    \namesection{Yaroslav}{Kulagin}{
        \faGithub\ \href{https://github.com/yaroslavprofi}{yaroslavprofi}\quad |\quad \faEnvelope\ \href{mailto:yaroslavprofi@yandex.ru}{yaroslavprofi@yandex.ru}\quad |\quad \faPhone\ +7 902 722-33-54
    }

    \begin{minipage}[t]{0.33\textwidth}
        \section{Education}

        \subsection{ITMO University}

        \descript{Bachelor of Computer Science}
        \location{Expected Jun 2023 | Saint Petersburg, Russia}
        Cumulative GPA: 94.265/100.0

        \sectionspace % Some whitespace after the section

        \subsection{Lyceum 14}
        \location{Graduated May 2019 with gold medal Tambov, Russia}

        \sectionspace % Some whitespace after the section

        \subsection{"Yandex lyceum"}
        \location{Graduated after 2 years of education}

        \sectionspace % Some whitespace after the section


        \section{Skills}

        \subsection{Programming languages}
        \vspace{0.5\topsep}

        \location{Intermediate}
        C++ \textbullet{} Python \textbullet{} Java \\
        \location{Novice}
        Kotlin \textbullet{} Clojure \textbullet{} JavaScript

        \sectionspace % Some whitespace after the section

        \subsection{Technologies}
        \vspace{0.5\topsep}

        \location{Collaborative development}
        Git \textbullet{} Github

        \sectionspace % Some whitespace after the section

        \subsection{Languages}
        % \vspace{0.5\topsep}
        \begin{itemize}[leftmargin=1em]
            \setlength\itemsep{0em}
            \item Russian --- Native
            \item English --- B2
        \end{itemize}

        % \sectionspace

        \sectionspace
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.6\textwidth}

        \section{Coding experience}

        \begin{itemize}[leftmargin=1em]
            \setlength\itemsep{0em}
            \item Python: I gained my entire Machine Learning experience using this language.
            I have experience with tensorflow, numpy, and scikit-learn.
            If you need to write something quickly and / or something compact, I resort to writing code in Python.
            Wrote games using pygame, communicated with telegram api and yandex maps.
            Created mafia bot in vk.
            \item Java: I studied for 2 years at school, where I created simple games of the type "3 in a row",
            and now I am studying at the university.
            \item Kotlin: Studied for 1 semester, at the end of which I created a client-server application:
            I wrote HTML and a Kotlin file generating Js, used a database for storage .pdf and hosted it all on AWS
            (unfortunately, the student account is no longer available and there is no access to the site,
            but the files are in my repository).
            \item C++: I studied at school from the 5th grade and at the university.
            I used it mainly for writing Olympiads and creating visualizations using Qt.
            \item Other: Writing .sh and .bat scripts, working with git, MarkDown + LaTex.
        \end{itemize}

        \sectionspace % Some whitespace after the section


        \section{Other experience}

        \begin{itemize}[leftmargin=1em]
            \setlength\itemsep{0em}
            \item Competitive programming: ACMP,  ICPC.
            \item Algorithms and Data Structures - 4 semesters: basic structures and algorithms,
            algorithms on graphs, tree structures, flow problem, basic knowledge of cryptography and number theory.
            \item Parsers, solution modularization, localization, concurrent programming on Java.
        \end{itemize}

        \sectionspace % Some whitespace after the section


        \section{Awards}

        \begin{itemize}[leftmargin=1em]
            \setlength\itemsep{0em}
            \item 2020 1\textsuperscript{st} --- Hakaton "Hack University", case 2, team - ArrayIndexOutOfBoundException
            \item 2020-2021, {3, 4}\textsuperscript{s} terms --- scholarship of the government of St. Petersburg
            \item 2021, 4\textsuperscript{s} term --- scholarship of Huawei
        \end{itemize}

        \sectionspace % Some whitespace after the section

    \end{minipage} % The end of the right column

\end{document}